msAggr_seurat

### 2021-11-03 msAggr_seurat/msAggr_seurat.Rmd
creating single script to streamline individual pop analyses
Adding code to generate 3D model

---
title: "msAggr_seurat"
output: 
  html_notebook: 
    fig_height: 6
---

@@

>>>>

---
title: "msAggr_seurat"
output:s
  html_document:
    df_print: paged
---

@@

# Generating 3D models
```{r}
rds.file <- "msAggr_seurat_dim26.RDS"
seurat.object <- readRDS(rds.file)
ndims <- as.numeric(gsub("[^0-9]", "", stringr::str_split(rds.file, "_")[[1]][3]))
```

```{r}
tot.var <- percent.variance(seurat.object@reductions$pca@stdev, plot.var = FALSE, return.val = TRUE)
ndims <- length(which(cumsum(tot.var) <= 90))
